\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../img/}}}

\begin{document}

\section*{Acknowledgments}

The whole Master program, as well as the research project underlying this thesis
was an extraordinary journey of my life, that gave me a lot of knowledge and lifelong
realizations. However, this journey would not be as pleasurable, or in some cases would not have been at all, unless specific people who were, are and will be in my life.

\vspace*{0.3cm}
First, this thesis is dedicated to my mother, Liana Iashvili. Her countless care and support has made it possible for me to achieve what I have achieved and to become the person I am today.

\vspace*{0.3cm}
I am immensely thankful to Prof. Richard Kempter for his support, guidance, and supervision throughout the completion of my master's thesis. I am greatful for an opportunity he gave me to work on such an interesting project, for his dedication, time, and all the knowledge and experience I acquired under his supervision. 

I am thankful to Prof. Marc Keßeböhmer, who aggreed to supervise me, and I am thankful for the insightful talks we had.

I thank Agnes for her tireless support during the whole master's program within and beyond the university life. I have many life-lasting sweet memories that would not have occurred without her. 
As sweet as all of the delicious cakes and cookies and dinners!
Thank you for always being there for us!

I am very grateful to my dear close, lifelong Foroogh, Katha, and Stefano. It is said, that finding a good friend is harder than finding a needle in a haystack. Though, against every odds in the universe, I have found three! Thank you for all your support and the unforgettable moments I shared with you. Without you, life would not be as bright as it is now. I would refrain myself from going into the details for what I am grateful to them, as the list will be much beyond the size of the thesis!

Finally, I would like to thank all my friends and family who I have not mentioned above. You have made my life happier and I'm glad I have all of you!

\end{document}